Classical Planning Algorithms ¡ on the Atari Video Games

### 2014-11-19 icaps15-paper/paper.tex
changed 35 to 48 games in abstract

\begin{abstract}
\begin{quote}
The Atari 2600 games supported in  the Arcade Learning Environment~\cite{bellemare:jair2013}
all feature a known initial (RAM) state and actions that have deterministic effects. Classical planners, however,
cannot be used  for selecting actions  for  two reasons: first,  no  compact PDDL-model of  the games is given,
and  more importantly,  the action effects and goals are  not known \emph{a priori}. Moreover, in these games there is usually
no set of goals to be achieved but rewards to be collected. These features do not preclude the use of   classical  algorithms like
breadth-first search or Dijkstra's algorithm,  but    these methods are not effective over  large state spaces. We thus turn to a
different class of classical planning algorithms  introduced recently  that perform a \emph{structured exploration} of the state space; namely,
like breadth-first search and Dijkstra's  algorithm they are ``blind'' and hence  do not require prior knowledge of state transitions,
costs (rewards) or goals, and yet, like  heuristic search algorithms, they have been shown to be   effective for solving   problems over huge
state spaces. The simplest such algorithm, called Iterated Width or \IW, consists of  a sequence of calls  $\IW(1)$, $\IW(2)$, \ldots,
$\IW(k)$ where  $\IW(i)$ is  a breadth-first search in which a state is  pruned when it is not the
first state in the search  to make true some subset of $i$ atoms. 
The  empirical results over 35 games suggest that the performance 
of \IW\ with the  $k$ parameter fixed to $1$, i.e., $\IW(1)$, is at the level of the state of the art represented by 
\UCT.  A simple best-first variation  of \IW\  that combines exploration and exploitation proves
to be very competitive as well. 
\end{quote}
\end{abstract}

>>>>

\begin{abstract}
\begin{quote}
The Atari 2600 games supported in  the Arcade Learning Environment~\cite{bellemare:jair2013}
all feature a known initial (RAM) state and actions that have deterministic effects. Classical planners, however,
cannot be used  for selecting actions  for  two reasons: first,  no  compact PDDL-model of  the games is given,
and  more importantly,  the action effects and goals are  not known \emph{a priori}. Moreover, in these games there is usually
no set of goals to be achieved but rewards to be collected. These features do not preclude the use of   classical  algorithms like
breadth-first search or Dijkstra's algorithm,  but    these methods are not effective over  large state spaces. We thus turn to a
different class of classical planning algorithms  introduced recently  that perform a \emph{structured exploration} of the state space; namely,
like breadth-first search and Dijkstra's  algorithm they are ``blind'' and hence  do not require prior knowledge of state transitions,
costs (rewards) or goals, and yet, like  heuristic search algorithms, they have been shown to be   effective for solving   problems over huge
state spaces. The simplest such algorithm, called Iterated Width or \IW, consists of  a sequence of calls  $\IW(1)$, $\IW(2)$, \ldots,
$\IW(k)$ where  $\IW(i)$ is  a breadth-first search in which a state is  pruned when it is not the
first state in the search  to make true some subset of $i$ atoms. 
The  empirical results over \numgames\ games suggest that the performance 
of \IW\ with the  $k$ parameter fixed to $1$, i.e., $\IW(1)$, is at the level of the state of the art represented by 
\UCT.  A simple best-first variation  of \IW\  that combines exploration and exploitation proves
to be very competitive as well. 
\end{quote}
\end{abstract}
